\documentclass[12pt]{article}
\usepackage{amsmath,amsfonts,amssymb}

\usepackage{diagbox}
\usepackage[colorlinks]{hyperref}

\usepackage{graphicx,caption,subcaption}

\usepackage{tikz}

\usepackage{url}
\urlstyle{tt}

\usepackage{geometry}
\geometry{%
  letterpaper,
  lmargin=1.5cm,
  rmargin=1.5cm,
  tmargin=2cm,
  bmargin=2cm,
  footskip=12pt,
  headheight=12pt}
 
 
\usepackage[parfill]{parskip}
\newcommand{\ATAN}{\operatorname{TAN}^{-1}}
\DeclareMathOperator{\COS}{COS}
 
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\headheight 35pt

\lhead{Mathcounts 2020}
\cfoot{\thepage}

\def\squarebox#1{\hbox to #1{\hfill\vbox to #1{\vfill}}}
\def\qed{\hspace*{\fill}
        \vbox{\hrule\hbox{\vrule\squarebox{.667em}\vrule}\hrule}}
\newenvironment{solution}{\begin{trivlist}\item[]{\bf Solution:}}
                      {\qed \end{trivlist}}


\def\a{{\alpha}}
\def\b{{\beta}}
\def\g{{\gamma}}
                   
\DeclareUnicodeCharacter{2212}{-}  

\begin{document}

\thispagestyle{empty}

\begin{center}\section*{Mathcounts 2020}

\end{center}


\begin{enumerate}

%18chapterteam 8
\bigskip
\item In isosceles right triangle ABC, AC = BC = 10 units.
The horizontal segments are spaced 1 unit apart, as are the vertical segments.
Including triangle ABC, how many of the triangles in this figure are isosceles right triangles?
%17s16
\bigskip
\bigskip
\item If x and y are integers such that $(x − 3)^2 + (y + 4)^2 = 25$, what is the greatest
possible value of $x^2 + y^2$?
%17s17
\bigskip
\bigskip
\item A positive integer q is the product of a prime number and a perfect square.
Additionally, q is the product of a different prime number and a perfect cube.
What is the least possible value of q?
%17s19
\bigskip
\item A pole of radius 1 inch and height h inches is perpendicular to the ground. A
snake is coiled around the pole in a spiral pattern, making a 60-degree angle
with the ground. If the snake is 9$\pi$ inches long and reaches from the ground to
the top of the pole, then h can be written in the form $a\pi\sqrt{b}$, where a is a rational
number and b is a positive integer that is not divisible by the square of any
prime. What is the value of a + b? Express your answer as a common fraction.
%17s22
\bigskip
\bigskip
\item Chloe finds a coin, wedged tightly into the corner of
her drawer behind a rectangular box with a 2.5-inch edge. One
corner of the box is 1.5 inches from the corner of the drawer and
the other corner of the box is 2 inches from the corner of the
drawer. What is the diameter of the coin?
%17s23
\bigskip
\bigskip

\item What four-digit number has tens digit 2 and units digit 8, is a multiple of 16, and
when its digits are reversed the result is also a multiple of 16?
%17s24
\bigskip
\item What is the radius of the inscribed circle of a triangle with side lengths 9, 13 and
14? Express your answer in simplest radical form.
%17s25 can't do' 26-30 print paper
%mock2017t8
\bigskip
\item Let ABC be a triangle with sides AB = 20, BC = 17, AC = 12 ,
and denote $\omega$ as the circumcircle of ABC . Let P be a point on the minor arc BC ,
and let K
be the foot of the altitude from P to BC such that BK = PK.
What is the ratio between the areas of  $\triangle$BPK to $\triangle$ABC ?
Express your answer as a decimal to the nearest thousandth.
%mock2016s29
\bigskip
\item How many paths of shortest length are there from A to B traveling along the line segments
on the 8 by 8 grid with a 2 by 2 square taken out of the center?
% 2019 team 10; 8, 9 need drawing
\bigskip
\item Amy and Rob are playing a dice game using a 10-sided fair die, with sides numbered 1 through 10.
Rob earns 3 points if the number rolled is prime, and Amy earns 2 points if the number rolled is even.
After 4 rolls, what is the percent
probability that Amy has won more points than Rob? Express your answer to the nearest hundredth.
% 2018 s19 needs drawing
% 2019 2018 2017 mistakes covered
%2016s16
\bigskip
\item The Beavers, Ducks, Platypuses and Narwhals are the only four basketball
teams remaining in a single-elimination tournament. Each round consists of the
teams playing in pairs with the winner of each game continuing to the next
round. If the teams are randomly paired and each has an equal probability of
winning any game, what is the probability that the Ducks and the
Beavers will play each other in one of the two rounds? Express
your answer as a common fraction.
%16national target 2
\bigskip
\item Set A consists of all integers a such that $a = p^2 – 1$, where p is a prime greater
than 3. What is the greatest common factor of all the numbers in set A?
% 2019 2018 2017 2016 mistakes covered
%15s18
\bigskip
\item The quadratic equation $x^2 + px + 2p = 0$ has solutions $x = a$ and $x = b$.
If the quadratic equation $x^2 + cx + d = 0$ has solutions $x = a + 2$ and $x = b + 2$,
what is the value of d ?
%15s22
\bigskip
\item Iniki has large, medium and small metal bars. The large bars each weigh 8 kg.
The medium bars each weigh 6 kg. The small bars each weigh 3 kg. Iron, nickel
and lead are present in the ratio 4:1:3 in each large bar, 2:1:3 in each medium
bar and 1:1:1 in each small bar. If Iniki wants to melt together a combination of
bars to make an alloy that contains 40 kg of iron, 20 kg of nickel
and 40 kg of lead, how many small bars will she have to use?
\bigskip
%15s23
\item If $x + \frac{1}{x} = 3$, what is the value of $x^4+\frac{1}{x^4}$?
%15s25
\bigskip
\item A restaurant sells three sizes of drinks: small for \$1.20, medium for \$1.30 and
large for \$1.80. Each person at a table of ten ordered one drink, for a total cost
of \$14.90, before sales tax. How many people ordered a large drink?
\bigskip
%15s27-30 print on paper
%15t7
\bigskip
\item When trying to recall some facts about the ages of his three aunts, Josh made the
following claims:
\begin{itemize}
\item Alice is fifteen years younger than twice Catherine’s age.
\item Beatrice is twelve years older than half of Alice’s age.
\item Catherine is eight years younger than Beatrice.
\item The three women’s ages add to exactly one-hundred years.
\end{itemize}
However, Josh’s memory is not perfect, and in fact only three of these four
claims are true. If each aunt’s age is an integer number of years, how old is
Beatrice?
\bigskip
%14s25
\item The diagonals of a parallelogram have lengths 82 cm and 30 cm. One altitude is
18 cm long. What is the smallest possible area of the parallelogram?
%16mocks9
\bigskip
\item   How many numbers between 1 and 25, inclusive, can be expressed as a sum of 2
distinct non-negative perfect squares?
\bigskip
%16mocks7
\item Let ABC be a right triangle with legs of integer lengths y and z, and
hypotenuse of length x. For how many ordered pairs (y,z) is the length of x
an irrational number between 4 and 6? (y,z) and (z,y) are considered distinct
ordered pairs.
\bigskip
%16 mock s 12
\item How many integers between 1 and 100, inclusive, cannot be multiplied by
a terminating decimal to get a product of 100?
\bigskip
%16 mock s 14
\item What is the last digit of $2016^{2016} + 1787^{1787}$?
%16 mock s17
\bigskip
\item Riders on a Ferris wheel travel in a circle in a vertical plane.
A particular wheel has radius 30 feet and revolves at the constant rate of
one revolution per minute. How many seconds does it take a rider to travel
from the bottom of the wheel to a point 15 vertical feet above the bottom?
%16 mock 18
\bigskip
\item George is making a list of all 606 four-letter permutations of the word “POTATOES”.
He then arranges the “words” in alphabetical order. Which position  is “AOPS” in?
For example, the word “AEOO” is in position 1.
%16 mock 23
\bigskip
\item  Given that
x+y+z=5, then the minimum value of xy+xz+yzcan be expressed as mn,
where mand n are relatively prime integers. What is the value of the expression m+n?
%16 mock s20
\bigskip
\item What is the second smallest positive integer that can be written as the sum of two
distinct positive integer squares in two different ways?
%16s30
\bigskip
\item A 12-sided game die has the shape of a hexagonal bipyramid, which consists of
two pyramids, each with a regular hexagonal base of side length 1 cm and with
height 1 cm, glued together along their hexagons. When this game die is rolled
and lands on one of its triangular faces, how high of the ground is the opposite
face? Express your answer as a common fraction in simplest radical form.

\bigskip
% 2019 2018 2017 2016 mistakes covered
%92state s30
\item  Digit d is randomly selected from set {4, 5, 6, 7}. without
replacement of d, another digit 3 is selected. What is the
probability that the two-digit number de is a multiple of 3?
Express your answer as a common fraction.
%90state s29
\bigskip
\item K is the smallest positive integer satisfying these properties:
\begin{itemize}
\item When K is divided by 5 the remainder is 4.
\item When K is divided by 8 the remainder is 2.
\item When K is divided by 11 the remainder is 1.
\end{itemize}
What is K?
% https://artofproblemsolving.com/community/c3h398285p2222096
% 1995 MathCounts State Team #8
% https://math.stackexchange.com/questions/757827/1995-mathcounts-state-team-8
\item In professional football it is possible to score 2 points
(for a safety), 3 points (for a field goal), or 6 points (for a touchdown).
If a touchdown is scored, it is possible to score one additional point. The score of a football
game is 21 to 17. Find the total number of possible combinations to achieve this final score.
% 2016 mock s28
\item   Every 2 digit positive integer is repeated 5 times and strung together (ex. 1818181818).
Find the remainder when all of these integers are added together and divided by 505
%99 s2
\item How many pairs of vertical angles are formed by five distinct lines that have a
common point of intersection?
%99sprint
\item What is the unit’s digit of $3^{84} - 7^{21}$?
%99 sprint
\item A solar system contains four planets.  
Planet A completes an orbit around the sun in 20 months;
Planet B completes an orbit in 36 months; Planet C completes an orbit in 40 months;
and Planet D completes an orbit in 48 months.  If the planets lie along a straight line
in May of the year 2000, what is the next year that they will again lie along the same line?
Assume the orbits are circular and that a year is 12 months long.
%16 s20
\item Diagonal XZ of rectangle WXYZ is divided into three segments each of length
2 units by points M and N. Segments MW and NY are parallel and are
both perpendicular to XZ. What is the area of WXYZ?
Express your answer in simplest radical form.
%16s21
\item A spinner is divided into 5 sectors. Each of the central
angles of sectors 1 through 3 measures 60 degrees while each of the
central angles of sectors 4 and 5 measures 90 degrees. If the spinner is
spun twice, what is the probability that at least one spin lands
on an even number? Express
%04s29 wrong
\item For six points (-1, 1), (-1,-1), (1, 1), (1,-1), (3, 1), (3,-1)
How many distinct circles of radius 2 units are in the
coordinate plan and pass through exactly two of the above points?
\bigskip
%05s21
\item How many positive three-digit integers with each digit greater
than 4 are divisible by 6?
\vspace{1cm}
%2015 done above
%05s18 is above
%2014 s25 is above; 26-30 printed out on paper
%2013 now done
%13 target 7
\item How many positive two-digit integers have exactly 8 positive factors?
\vspace{1cm}
%13s22
\item In some languages, every consonant must be followed by a vowel. How many
seven-letter ``words" can be made from the Hawaiian word MAKAALA if each
consonant must be followed by a vowel?
%13s28
\vspace{1cm}

\item The game of Connex contains one 4-unit piece, two identical 3-unit pieces, three
identical 2-unit pieces and four identical 1-unit pieces. How many different
arrangements of pieces will make a 10-unit segment?
%13s29
\vspace{1cm}

\item In square units, what is the largest possible area a rectangle inscribed in the
triangle with sides 10, 17 and 21?
%13s30
\vspace{1cm}

\item A line segment with endpoints A(3, 1) and B(2, 4) is rotated about a point in
the plane so that its endpoints are moved to A' (4, 2) and B' (7, 3), respectively.
What are the coordinates of the center of rotation? Express your answer as an
ordered pair.
\vspace{1cm}

%12s25
\item A triangle has angles measuring 15-deg, 45-deg and 120-deg. The side opposite the 45-deg
angle is 20 units in length, and the area of the triangle can be expressed in
square units as $(m − n \sqrt{q})$, where q is a prime number. What is the value of
the sum m + n + q?
%2012 done; printed out s26-30
\vspace{1cm}

%11s12
\item Javier needs to exchange his dollar bill for
coins. The cashier has 2 quarters, 10 dimes
and 10 nickels. Assuming the cashier gives
Javier the correct amount and at least one
quarter, how many possible combinations of
coins could Javier receive?
\vspace{1cm}
%11s20
\item When the diameter of a pizza increases by 2 inches, the area
increases by 44\%. What was the area, in square inches, of
the original pizza? Express your answer in terms of $\pi$.
\vspace{1cm}
%11s23
\item A right circular cone is sliced into four pieces
by planes parallel to its base. All of these pieces have the same
height. What is the ratio of the volume of
the second-largest piece to the volume of
the largest piece? Express your answer as a
common fraction.
\vspace{1cm}
%11t5
\item How many distinct sums can be obtained by adding three
different numbers from the set \{3, 6, 9. ..., 27, 30\}?
%11 s27-30 print on paper
\vspace{1cm}
%1819 HB 249 250
\item Notice that 2019 can be written as the sum of consecutive integers in increasing order in numerous ways, for example 1009 +1010 = 2019 and (−2018) + (−2017) + ... + 2018 + 2019 = 2019. Including these two examples, in how many ways can 2019 be written as the sum of at least two consecutive integers in increasing order?
\vspace{1cm}
%1819 HB 249 250
\item Three parallel chords of lengths 12, k and 16 units are in a circle.
If the chord of length k is equally spaced 2 units away from each of the other chords, what is the value of k? Express your answer in simplest radical form.
\vspace{1cm}

% year 2011 done
%2010 chapter s29

\item In triangle ABC, AB = AC and D is a point on AC so that
BD bisects angle ABC. If BD = BC, what is the measure, in
degrees, of angle A?

\vspace{1cm}

%10 state s5
\item The points (4, 0) and (−4, 0) are two non-consecutive vertices
of a rhombus with an area of 80 square units. One of the other
vertices is (0, K) where K > 0. What is the value of K?
\vspace{1cm}

%10 target 2
\item How many subsets of the set \{M, A, T, H, C, O, U, R, S, E\}
contain at least one vowel?
\vspace{1cm}

%10t6
\item Trapezoid ABCD has base AB = 20 units and base
CD = 30 units. Diagonals AC and BD intersect at X. If the
area of trapezoid ABCD is 300 square units, what is the area of
triangle BXC?
\vspace{1cm}
%10t8
\item A belt is drawn tightly around three circles of radius 10 cm
each. The length of the belt, in cm, can be written in
the form a + b$\pi$. What is the value of a + b?

%10year done, 09 next
%09 target 2
\vspace{1cm}
\item Two arithmetic sequences A and B both begin with 30 and
have common differences of absolute value 10, with sequence
A increasing and sequence B decreasing. What is the absolute
value of the difference between the 51st term of sequence A
and the 51st term of sequence B?
%09 sprint 2
\vspace{1cm}
\item The Golden Chicken Egg Farm packages eggs
in cartons that hold 12 eggs each. What is the
smallest number of eggs greater than
10,000 that will fill an integer number of these
cartons without any eggs left over?
\vspace{1cm}

%09s29

\item The sum of n positive integers, not necessarily distinct, is 22. What
is the largest possible product of the n integers?

%09 s28
\vspace{1cm}
\item Points X, Y and Z lie on the sides of triangle ABC so that segments
AX, BY and CZ, if drawn, would intersect at one interior point P.
Using 3 of these 7 points at a time as vertices, how many triangles
can be formed?

%09 sprint 5
\vspace{1cm}
\item A flock of geese is swimming on a peaceful
lake when a noisy motorcycle drives past causing
$\frac{2}{5}$ of the geese to fly away. A little later a small
herd of deer runs past and causes $\frac{1}{3}$ of the
remaining geese to fly off. Then when a loud
siren sounds, another 24 geese leave the lake.
Now only 46 geese remain on the lake. How
many geese were there in the flock at the start?
%09 sprint 6
\vspace{1cm}
\item The probability it will rain on Saturday
is 60\%, and the probability it will rain
on Sunday is 25\%. If the probability of
rain on a given day is independent of
the weather on any other day, what is
the probability it will rain on both days,
expressed as a percent?
\vspace{1cm}
%09 s23
\item An isosceles right triangle is removed from each
corner of a square piece of paper, to
create a rectangle whose diagonal is AB. If AB = 12 units, what is the
combined area of the four removed triangles, in
square units?
\vspace{1cm}
%09 s24
\item If $1 \le a \le 10$ and $1 \le b \le 36$, for how many ordered pairs of
integers (a, b) is $\sqrt{a + \sqrt{b}}$  an integer?

%09s27
\vspace{1cm}

\item An integer X has the following properties:
\begin{enumerate}
\item X is a multiple of 17
\item X is less than 1000
\item X is one less than a multiple of 8.
\end{enumerate}
What is the largest possible value of X?

%09 s30 is circle + triangle; circle angle jumping technique

%08s3
\vspace{1cm}

\item What is the greatest number of interior right angles a convex
octagon can have?
\vspace{1cm}

%08t2;
\item Bill is sent to a donut shop to purchase exactly six donuts. If the shop has four kinds of donuts and Bill is to get at least one of each kind, how many combinations will satisfy Bill’s order requirements?
\vspace{1cm}

\item For how many non-negative real values of x is $\sqrt{144 − \sqrt[\leftroot{-1}\uproot{2}\scriptstyle 3]{x}}$ an
integer?

%11t2;
\vspace{1cm}

\item An employee of a delivery company drives 480 miles at
60 miles per hour in a vehicle that averages 20 miles per gallon
of gas. The employee is paid \$12 per hour, gasoline costs \$3
per gallon, and maintenance on the vehicle is \$0.15 per mile.
According to these rates, what is the total cost of this trip for
the company?
\vspace{1cm}

%07s1
\item In a figure a largest circle has
a radius of six meters. Five congruent smaller
circles are placed inside and are lined up in
east-to-west and north-to-south orientations.
What is the radius of one of the five smaller
circles?

%08 07 still needs to be done
\vspace{1cm}
%08s11

\item Jim’s stride measures $2\frac{1}{2}$
feet, and Jeffrey’s stride measures $2\frac{2}{3}$
feet. There are 5280 feet in a mile. If Jim and Jeffrey each
walk one mile, what is the ratio of the number of strides Jim
takes to the number of strides Jeffrey takes? Express your
answer as a common fraction.
%08s15
\vspace{1cm}

\item The integers from 1 through 15 are written in numerical order in
pencil going clockwise around a circle. A student begins moving
clockwise around the circle erasing every third integer that has
not yet been erased until only the integer 11 remains. Which
integer did the student erase first?
%08s22

\item The first term of an arithmetic sequence is 1, another term of the
sequence is 91 and all of the terms of the sequence are integers.
How many distinct arithmetic sequences meet these three
conditions?
%08s23
\vspace{1cm}

\item A circular cylindrical post with a circumference of
4 feet has a string wrapped around it, spiraling from the
bottom of the post to the top of the post. The string evenly
loops around the post exactly four full times, starting at the
bottom edge and finishing at the top edge. The height of the
post is 12 feet. What is the length, in feet, of the string?
\vspace{1cm}

%08s24
\item The areas of two squares differ by 100 square units, and the
perimeters of the two squares differ by 10 units. What is the
perimeter, in units, of the smaller square?

\vspace{1cm}

%08t4
\item  Kendra has an unlimited supply of unbreakable sticks of
length 2, 4 and 6 inches. Using these sticks, how many non-congruent
triangles can she make? Two sticks can be joined only at a vertex of
the triangle. (A triangle with sides of length 4, 6, 6 is an example
of one such triangle to be included.)
%08t6
\vspace{1cm}
\vspace{1cm}

\item In a six-team softball league, each team played each other team
exactly once during the season. No game ended in a tie. At the end of the season,
n teams had the same best record. What is the maximum possible value of n?

%08t8
\item To transmit a positive integer less than 1000, the Networked Number Node
offers two options.
\begin{itemize}
\item Option 1:   Pay \$d to send each digit d.
Therefore, 987 would  cost \$9 + \$8 + \$7 = \$24 to transmit.
\item Option 2:  Encode integer into binary (base 2) first, and then
pay \$d to send each digit d.  Therefore, 987 becomes 1111011011 and would
cost \$1 + \$1 + \$1 + \$1 + \$0 + \$1 + \$1 + \$0 + \$1 + \$1 = \$8.
\end{itemize}
What is the largest integer less than 1000 that costs the same whether
using Option 1 or Option 2?
\vspace{1cm}
%08 done; 07 now
%07t4
\item In how many ways can 36 be written as the product
$a \times b \times c \times d$, where a, b, c and d are positive integers such
that $a \le b \le c \le d$?
\vspace{1cm}
%07t5
\item The first square below is in position ABCD. After rotating the
square 90 degrees clockwise about its center point, the second
square is in position DABC, as shown. Next, square DABC
is reflected over its vertical line of symmetry, resulting in the
third square in position CBAD. If the pattern of alternately
rotating 90 degrees clockwise and reflecting over the vertical
line of symmetry continues, in what position will the 2007th
square be? Write your answer starting with the lower left
vertex and continuing clockwise with the other three vertices.
%07t7
\vspace{1cm}

\item When the expression $(2^1)(2^2)(2^3)...(2^{99})(2^{100})$ is written as an
integer, what is the product of the tens digit and the ones digit?

\vspace{1cm}

%07s8
\item How many perfect squares less than 1000 have a ones digit of
2, 3 or 4?

\vspace{1cm}
%07s13
\item In this quilt pattern, points E, F, G and H are
midpoints of the sides of square ABCD, and
square EFGH is divided into nine congruent
unit squares, four of them shaded.
What percent of the
total area of square ABCD does the total
shaded area represent? Express your answer
to the nearest whole percent.
\vspace{1cm}
%07s17
\item What is the greatest number of whole 4-inch by 6-inch notecards
that can be cut from a 25-inch by 27-inch sheet of poster board if
every cut must be made parallel to a side of the poster board? No
taping or gluing is allowed.
\vspace{1cm}
%07s18
\item Brand X soda advertises, “We will give you 20% more soda
than Brand Y for a total price that is 10% less than Brand Y’s
price!” What is the ratio of the unit price of Brand X soda to the
unit price of Brand Y soda? Express your answer as a common
fraction.
\vspace{1cm}
%07s19
\item A “size 2 square of squares” is a 2 by 2 grid of digits where the
digits in each row, from left to right, form a two-digit perfect
square, and the digits in each column, from top to bottom, also
form a two-digit perfect square. How many “size 2 squares of
squares” are there?
\vspace{1cm}
%07s23
\item A box contains some green marbles and exactly four red marbles.
The probability of selecting a red marble is x\%. If the number of
green marbles is doubled, the probability of selecting one of the
four red marbles from the box is (x - 15)\%. How many green
marbles are in the box before the number of green marbles is
doubled?
\vspace{1cm}
%07s26 need drawing
%\item The area of the semicircle in Figure A
%is half the area of the circle in
%Figure B. The area of a square
%inscribed in the semicircle, as shown,
%is what fraction of the area of a square inscribed in the circle?
%Express your answer as a common fraction.

%03 01 00 not done; 99 done; 98 not done
\vspace{1cm}

%03t4
\item A cube is sliced by a plane which goes through two opposite
corners and the midpoints of two edges. If the cube
has edge length one unit, how many square units are in the area
of the rhombus formed by the intersection of the plane and the
cube? Express your answer as a common fraction in simplest
radical form.
\vspace{1cm}

%03s10
\item Points P and R are located at (1, 3) and (7, 15) respectively.
Point M is the midpoint of segment PR. Segment PR is
reflected over the x-axis. What is the sum of the coordinates of
the image of point M (the midpoint of the reflected segment)?
%03s11
\vspace{1cm}

\item In a three-digit number, the hundreds digit is greater than 5, the
tens digit is greater than 4 but less than 8, and the units digit is
the smallest prime number. How many three-digit numbers
satisfy all of these conditions?
\vspace{1cm}
%03s14
\item Each of the four digits 2, 4, 6 and 9 is placed in one of the
boxes to form a fraction with two digits up and two digits down.
The numerator and
the denominator are both two-digit whole numbers. What is
the smallest value of all the common fractions that can be
formed? Express your answer as a common fraction.
\vspace{1cm}

%03s24; s15-17 printed out

\item Three fair, standard six-faced dice of different colors are rolled.In how many ways can the dice be rolled such that the sum ofthe numbers rolled is 10?

\vspace{1cm}

%03 done; 01 00 not done; 99 done; 98 not done; 01 can't copy and paste any more
%01s5

\item There are 12 eggs in a carton, 8 cartons in a crate, and 9 crates in a container.
How many eggs are in a container?

\vspace{1cm}
%s06s22

\item The sum of five different positive integers is 320. The sum of
the greatest three integers in this set is 283. The sum of the
greatest and least integers is 119. If x is the greatest integer
in the set, what is the positive difference between the greatest
possible value and least possible value for x?
\bigskip
\vspace{1cm}

%05s21 wrong
\item How many positive three-digit integers with each digit greater
than 4 are divisible by 6?
%04s29 wrong
\vspace{1cm}

\item For six points (-1, 1), (-1,-1), (1, 1), (1,-1), (3, 1), (3,-1)
How many distinct circles of radius 2 units are in the
coordinate plan and pass through exactly two of the above points?
\vspace{1cm}


%93t2
\item Alfreda hiked half her planned trip the first day; tiring, she only
covered one-third the remaining distance the second day; rain slowed her to one-fourth
the remaining distance the third day, and the fourth day she hiked three miles,
which was on fifth of what she had left after the third day. How many miles did she hike during
the four days.
\vspace{1cm}

%railroad trestle 91t8 wrong
\item A railroad trestle spans a gorge 80 feet wide
and connects two cliffs at heights 112 feet and 172 feet above the bottom of the gorge.
A train is crossing this gorge from the higher cliff to the lower. When the front of
the train has traveled $\frac{3}{4}$ of the trestle’s length, how many feet is it above the bottom of
the gorge?
\vspace{1cm}
%91t6
\item A circular sheet of paper of radius 6 inches is cut into 3 equal sectors
and each sector is
formed into a cone with no overlap. What is the height, in inches, of each cone?

\end{enumerate}
\end{document}

